\thesistitle

### 2019-11-22 pldi/paper.tex
Bla

To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection.

@@

\subsubsection{Subtree}
A third approach to compare blocks of code is to compare subtrees of the AST of the source code. The advantage of this is that the result may be more useful for refactoring, as clones that are found are often easier to refactor. The disadvantage is that some clones may not be found. An example of this is shown in Fig.~\ref{fig:subtreecomparison}.

@@

\subsection{Search Root}

\subsection{Exclusions}

\subsection{Compare Rules}

>>>>

To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection. \todo{finish this}

@@

\subsubsection{Subtree}
A third approach to compare blocks of code is to compare subtrees of the AST of the source code. The advantage of this is that the result may be more useful for refactoring, as clones that are found are often easier to refactor. The disadvantage is that some clones may not be found. An example of this is shown in Fig.~\ref{fig:subtreecomparison}. In this figure, both the for-loop and the if-statement do not match completely between the two fragments. Because of that, when comparing subtrees, both would not indicate a match.

@@

\subsection{Search Root}
Some clone detection tools only search for clones inside of method bodies \cite{ragkhitwetsagul2019siamese}. To allow for such targeted analyses, we introduce the \textbf{SearchRoot} keyword into CDD. This keyword determines where the script will start looking for clones. For instance, if we want to limit our analysis to methods and constructors, we can specify the following:

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent\textbf{\textcolor[HTML]{7F0055}{SearchRoot}} MethodDeclaration, ConstructorDeclaration \\
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

The \textit{SearchRoot} keyword takes as an argument a comma separated list of nodes. The names that are being used here, \textit{MethodDeclaration} and \textit{ConstructorDeclaration}, are the names of the method and constructor declaration nodes. The names of these nodes can be the name of any node specified in the JavaParser library \cite{tomassetti2017javaparser}. This is because CDD uses JavaParser under the hood to parse an AST and perform clone detection.

\subsection{Exclusions}
Type 2 clones allow variance in identifiers and literals. To allow to exclude nodes in CDD, there is the \textbf{DoNotCompare} keyword. This keyword allows to specify a list of nodes that should be excluded from matching.
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent \textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr \\
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
This keyword is different from the \textit{Exclude} keyword in that the \textit{Exclude} keyword specifies nodes that will not be included in clones, whereas \textit{DoNotCompare} nodes will be included in clones but do not have to match for them to be considered a clone.

\subsection{Compare Rules}
Finally, CDD allows to specify any number of compare rules. The syntax for these rules is simple but powerful. \todo{explain}
